\propertitle

### 2019-07-10 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-10T14:04:12+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\newcommand*{\yR}{\bm{R}}

@@

We therefore want to assess how well the maximum-entropy distributions of
\fig~\ref{fig:plots_6mom} answer our two questions above. We do this by
sampling from the probability density $\pf(\yF \| \yD \yI)$ through
Markov-chain Monte Carlo. The density is
\begin{equation}
  \label{eq:density_proportional}
  \pf(\yF \| \yD \yI) \propto
  \Nd(\ycm\yF \| \yc, \ycs)\;
  \Nd(\yd\yF \| 0, \yds)\;
  \exp[-\yL\;\ysh(\yF;\yR)]
\end{equation}

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-07-10T21:31:16+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

\newcommand*{\yRR}{R}
\newcommand*{\yR}{\bm{\yRR}}

@@

Let's therefore examine the full density $\pf(\yF \| \yD \yI)$ given by the
probability calculus. Its derivation is given in appendix***; here we
briefly discuss its mathematical features and examine the answers it
provides. Its form is this:
\begin{equation}
  \label{eq:density_proportional}
  \pf(\yF \| \yD \yI) \propto
  \Nd(\ycm\yF \| \yc, \ycs)\;
  \Nd(\yd\yF \| 0, \yds)\;
  \exp[-\yL\;\ysh(\yF;\yR)]
\end{equation}
and the three main terms have the following meaning:

$\exp[-\yL\;\ysh(\yF;\yR)]$ expresses our pre-data uncertainty about the
possible frequency distributions. Here
$\ysh(\yF;\yR)\defd \sum_{\yA}\yFF_{\yA}\ln\frac{\yFF_{\yA}}{\yRR_{\yA}}$
is the relative entropy or discrimination information
\citep{kullback1987,jaynes1963,hobson1969,hobsonetal1973}, $\yR$ is a
reference distribution, and $\yL$ a positive parameter. This density is
proportional to the number of ways in which the frequency distribution
$\yF$ can be realized if we assume that the activities appear with
frequencies $\yR$ in the long run, as can be seen using Stirling's
approximation. For $\yR$ we use the uniform distribution, but any
biologically sensible distribution, which gives higher frequencies to low
activities, leads to the same final results. The parameter $\yL$ roughly
corresponds to the number of data points necessary to change our initial
belief, and we set it equal to $50$. \mynote{connection with entropic
  priors
  \citep{rodriguez1991,skilling1998,catichaetal2004,neumann2007,portamana2017}
}

$\Nd(\yd\yF \| 0, \yds)$ expresses our belief, hinging on biological
arguments, that the frequency distribution should be somewhat smooth: if
the activity levels $\yA-1$ and $\yA+1$ appear roughly equally often, we
don't believe that the activity $\yA$ could appear with an extremely
different frequency than theirs. The matrix $\yd$ is the discrete
equivalent of a fourth-order derivative \mynote{ref}; the probability of
its squared integral decreases exponentially with standard deviation
$\yds$. We set this such that the smoothness of the maximum-entropy
distribution is within two standard deviations, thus allowing for more
maxima and minima in $\yF$.

The two densities above together express our pre-data beliefs about the
possible frequency distributions.

$\Nd(\ycm\yF \| \yc, \ycs)$ ***
